---
title: "Mass Shooting Data"
author: Jayr Gudino
output: html_document
---

```{r echo=FALSE, message=FALSE}
source("/Users/jayrg007/Desktop/INFO201/a5-b-JayrG007/analysis.R")
library(ggplot2)
library(knitr)
library(kableExtra)
```
## Summary Information

Original Data Source [Here](https://www.gunviolencearchive.org/reports/mass-shooting?year=2018)

In 2018, mass shootings around the country were not slowing down, in fact, there were a total of **`r total_events`** mass shootings, according to the gun violence archive.

The total amount of lives lost was just shy of 400 people, `r total_lives_lost` to be exact.

The total amount of people injured was substantially greater than the amount of people killed, which was `r total_people_injured`.

The city that was the most impacted was `r city_most_impacted`, with `r num_killed_in_city` lives lost. 

Interestingly enough, the second most impacted city was across the country.

## Summary Table
The table below shows the totals and averages for the number of people killed and injured during 2018 mass shootings.
```{r, echo=FALSE} 
kable(summary_table) %>%
  kable_styling(bootstrap_options = c("striped"))
```

## Parkland Shooting
One particular incident was the Parkland Shooting, in `r parkland_incident`, on `r parkland_date`.

The number of people killed was `r num_killed_in_parkland`, and the number of people injured was `r num_injured_in_parkland`.

For more information on this incident click [here](https://www.nbcnews.com/news/us-news/police-respond-shooting-parkland-florida-high-school-n848101).

## Map of shootings in 2018
This map places markers on locations where mass shootings took place.

```{r echo=FALSE, warning=FALSE, message=FALSE}
map_of_shootings
```
As we can see, more mass shootings took place on the right side of the country, than 
on the left side of the country.

And also, there is a big gap in the middle, which is really interesting, to say the least. And there were also only three incidents last year in our state, Washington State.


## Plot of number of people killed in each state
How do the amount of people killed in each state, compare to each other?

This plot will give us an idea.


```{r echo=FALSE, message=FALSE}
shooting_plot
```


And as we can see, the the state with the highest amount of people killed was Florida, with California being a close second.

Also, there were several states that had shooting incidents, but no one died, thankfully.
